### 2016-08-24 analysis-note-v2/Appendix.tex
update the free proton interpolation chapter in the appendix.

>>>>

\section{Summary}
In this analysis we use the interpolated values from fitting the experimentally 
measured free proton asymmetries to construct the beam-spin asymmetry ratios.  
The differences between the beam-spin asymmetry ratios calculated using the 
fitting the free proton asymmetries and the model-dependent interpolated values 
were added as a systematic errors on the constructed beam-spin asymmetry 
ratios. Table \ref{table:ALU_ratios_} presents the coherent and the incoherent 
$A_{LU}$ ratios extracted using both methods and the associated systematic 
uncertainties.

\small
\begin{landscape}
\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l|l|l||}
         \hline
 ($Q^{2}$, $x_{B}$, $-t$) & EG6 $A_{LU}$ $\pm$ stat. &  Exp. fit $\pm$ stat. & Exp. $A_{LU}$ ratio   &  Model extr. & Model $A_{LU}$ ratio &  Diff. (Exp - Model)    \\
  \hline
(1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027   &    0.174 $\pm$ 0.030   & 0.781213 $\pm$ 0.171565   &  0.2050 &  0.6634 &  0.1178 \\
(1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033   &    0.217 $\pm$ 0.046   & 0.71823  $\pm$ 0.171458   &  0.2244 &  0.6951 &  0.0231 \\ 
(2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038   &    0.220 $\pm$ 0.056   & 0.702512 $\pm$ 0.195657   &  0.2177 &  0.7110 &  0.0084 \\
(3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042   &    0.184 $\pm$ 0.061   & 0.665608 $\pm$ 0.254408   &  0.2017 &  0.6088 &  0.0568 \\
  \hline \hline  \hline                                                                                        
(1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026   &    0.172 $\pm$ 0.029   & 0.687175 $\pm$ 0.164567   &  0.1885 &  0.6302 &  0.0569 \\
(1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029   &    0.222 $\pm$ 0.045   & 0.805541 $\pm$ 0.157091   &  0.2135 &  0.8379 &  0.0323 \\
(2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036   &    0.230 $\pm$ 0.057   & 0.657427 $\pm$ 0.179755   &  0.2170 &  0.6972 &  0.0397 \\
(2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050   &    0.163 $\pm$ 0.057   & 0.808622 $\pm$ 0.342802   &  0.2103 &  0.6281 &  0.1805 \\
  \hline  \hline  \hline                                                                                       
(1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027   &    0.238 $\pm$ 0.070   & 0.61362  $\pm$ 0.147379   &  0.2438 &  0.6013 &  0.0123 \\
(2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031   &    0.280 $\pm$ 0.061   & 0.536143 $\pm$ 0.125386   &  0.2410 &  0.6248 &  0.0886 \\
(2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039   &    0.229 $\pm$ 0.056   & 0.711628 $\pm$ 0.192687   &  0.2195 &  0.7425 &  0.0308 \\
(2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054   &    0.080 $\pm$ 0.029   & 1.42796  $\pm$ 0.72146    &  0.1235 &  0.9311 &  0.4968 \\
  \hline  \hline  \hline                                                                                         
(1.143, 0.132, 0.096) &  0.332 $\pm$ 0.051   &    0.162 $\pm$ 0.039   & 2.04913  $\pm$ 0.405462   &  0.2447 &  1.3596 &  0.6895 \\
(1.423, 0.170, 0.099) &  0.353 $\pm$ 0.051   &    0.186 $\pm$ 0.057   & 1.89763  $\pm$ 0.404796   &  0.2518 &  1.4050 &  0.4926 \\
(1.902, 0.224, 0.107) &  0.258 $\pm$ 0.050   &    0.189 $\pm$ 0.094   & 1.36191  $\pm$ 0.431827   &  0.2359 &  1.0941 &  0.2678 \\
    \hline \hline  \hline                                                                                      
(1.164, 0.132, 0.095) &  0.373 $\pm$ 0.073   &    0.160 $\pm$ 0.038   & 2.33093  $\pm$ 0.535511   &  0.2234 &  1.6696 &  0.6613 \\
(1.439, 0.170, 0.099) &  0.267 $\pm$ 0.086   &    0.186 $\pm$ 0.057   & 1.43489  $\pm$ 0.515672   &  0.2432 &  1.0978 &  0.3370 \\
(1.844, 0.225, 0.107) &  0.362 $\pm$ 0.092   &    0.188 $\pm$ 0.095   & 1.92214  $\pm$ 0.689863   &  0.2515 &  1.4421 &  0.4800 \\
     \hline  \hline  \hline                                                                                    
(1.493, 0.177, 0.1)   &  0.326 $\pm$ 0.030   &    0.189 $\pm$ 0.061   & 1.721    $\pm$ 0.322757   &  0.2453 &  1.3289 &  0.3921 \\                                                                 
 \hline
 \end{tabular}
 \caption{$A_{LU}$ ratios. The first three blocks stand for the incoherent bins 
 in $Q^{2}$, $x_{B}$, and $-t$, respectively. The last three blocks are for the 
 coherent bins in $Q^{2}$, $x_{B}$, and $-t$, respectively. The first column 
 contains the mean value of the kinematical variables for each bin. The second 
 column contains EG6 measured $A_{LU}$ with the statistical error bars. The 
 third column ("Exp. fit $\pm$ stat.") contains the interpolated free proton 
 $A_{LU}$ at EG6 kinematical values from fitting the free proton beam-spin 
 asymmetries. The forth column ("Exp. $A_{LU}$ ratio") stands for the 
 calculated $A_{LU}$ ratios using EG6 asymmetries and the fitted free proton 
 asymmetries. The fifth column ("Model extr.") stands for the model-depended 
 extracted free proton asymmetries. The sixth column ("Model $A_{LU}$ ratio") 
 presents the calculated $A_{LU}$ ratios using EG6 asymmetries and the 
 model-dependent extracted free proton asymmetries. The last column ("Diff.  
 (Exp - Model)") shows the difference between the two calculated $A_{LU}$ 
 ratios for each bin.}
 \label{table:ALU_ratios_}
 \end{center}
\end{table}
\end{landscape}
